---
title: 'Milestone #4'
author: "Niel Schrage"
date: "2/26/2020"
output: bookdown::pdf_document2
bibliography: [basicbib.bib]
biblio-style: "apalike"
link-citations: false
toc: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading libraries

library(tidyverse)
library(bookdown)
library(tinytex)
library(gt)
library(gtsummary)
library(stargazer)
library(knitr)


pdf_document2()


```

# Milestone #4

This is the fourth milestone for my final replication project for Gov 1006.^[Gov 1006: Models, this is an example of a footnote.] My github repository can be found here.^[https://github.com/nschrage/replication_2]

I am now replicating ["What the Demolition of Public Housing Teaches Us about the Impact of Racial Threat on Political Behavior"](https://onlinelibrary.wiley.com/doi/abs/10.1111/ajps.12156), by Ryan D. Enos. The central research question of this paper is, dow does the context in which a person lives affect his or her political behavior [@paper]? Professor Enos has provided his replication data [@data].  

Here is an example of a table made using GT:

```{r gt, echo = FALSE}

data.1 <- data.frame(a = sample(10:20, 8, replace = TRUE), b = sample(10:20, 8, replace = TRUE), c = sample(10:20, 8, replace = TRUE)) 

gt(data.1) 

# kable(x = data.1, caption = "A Simple Table", position = "!h")



```


Here is an example of a regression table made using GT Summary:

```{r regression, echo=FALSE}

data2 <- data.frame(a = sample(10:20, 8, replace = TRUE), b = sample(10:20, 8, replace = TRUE), c = sample(10:20, 8, replace = TRUE))

mod.1 <- lm(data2$b ~ data2$a) 

t1 <- tbl_regression(mod.1) 

t1




```

# Milestone #5

**turning these in LATE, but working on them**

# Milestone #6

Appendix: 

A clear statement about what aspects of the paper you were able to replicate and which parts, if any, you were not able to replicate.

500 words about your proposed extension. You do not have to have done the extension yet.

Selected Bibliography + References: 
    
